---
title: "721 BRFSS 2022"
author: "Ilmul Jahan Tani"
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(haven)
library(dplyr)
library(car)
library(janitor)
library(ggplot2)
library(gtsummary)
library(labelled)
library(flextable)
library(lme4)
library(lmerTest)
library(survey)
library(flextable)
```


```{r}
dat12 <- read_xpt("C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\LLCP2012.XPT") %>% 
  janitor::clean_names()
```

```{r}
names(dat12)
```

```{r}
dat12a <- dat12 %>% 
          dplyr::select(state, intvid, seqno, imonth, iday, iyear, dispcode, psu, ststr, llcpwt, geostr, wt2, strwt, sex, age, racegr2, marital, educa, employ, genhlth, addepev2, exerany2, cvdcrhd4, hlthpln1)

names(dat12a)
```

```{r}
summary(dat12a)
```

#interview final result (needs recoding?)
```{r}
class(dat12a$dispcode)
table(dat12a$dispcode, useNA = "always") #1100:completed, 1200: partial
summary(dat12a$dispcode)
```

#selecting only the completed interviews
```{r}
dat12b <- dat12a %>% 
  filter(dispcode==1100 & iyear==2012)
```

#state (remove some states??)
```{r}
class(dat12b$state)
table(dat12b$state)
```

#intvid
```{r}
class(dat12b$intvid)
dat12b$intvid <- as.numeric(dat12b$intvid, na.rm=T)
table(dat12b$intvid, useNA = "always")
summary(dat12b$intvid)
#61502 NAs
```

#seqno
```{r}
class(dat12b$seqno)
table(dat12b$seqno, useNA = "always")
summary(dat12b$seqno)
#no missing
```

#interview day
```{r}
class(dat12b$iday)
dat12b$iday <- as.numeric(dat12b$iday)
table(dat12b$iday, useNA = "always")
summary(dat12b$iday)
#no missing
```

#interview month
```{r}
class(dat12b$imonth)
dat12b$imonth <- as.numeric(dat12b$imonth)
table(dat12b$imonth, useNA = "always")
summary(dat12b$imonth)
#no missing
```

#interview year
```{r}
class(dat12b$iyear)
dat12b$iyear <- as.numeric(dat12b$iyear)
table(dat12b$iyear, useNA = "always")
summary(dat12b$iyear)
```

#sex
```{r}
class(dat12b$sex)
table(dat12b$sex, useNA = "always") 
summary(dat12b$sex)
#no missing
```

#age
```{r}
class(dat12b$age)
table(dat12b$age, useNA = "always") 
summary(dat12b$age)
#no missing
```

#race
```{r}
class(dat12b$racegr2)
table(dat12b$racegr2, useNA = "always") 
summary(dat12b$racegr2)
#88 missing
```

#marital status (needs recoding)
```{r}
class(dat12b$marital)
table(dat12b$marital, useNA = "always") 
summary(dat12b$marital)

#missing
```

#education level (needs recoding)
```{r}
class(dat12b$educa)
table(dat12b$educa, useNA = "always") 
summary(dat12b$educa)
```

#employment (needs recoding)
```{r}
class(dat12b$employ)
table(dat12b$employ, useNA = "always") 
summary(dat12b$employ)
```

#General health (needs recoding)
```{r}
class(dat12b$genhlth)
table(dat12b$genhlth, useNA = "always") 
summary(dat12b$genhlth)

#missing
```

#Have depression (needs recoding)
```{r}
class(dat12b$addepev2)
table(dat12b$addepev2, useNA = "always") 
summary(dat12b$addepev2)

#missing
```

#Exercise
```{r}
class(dat12b$exerany2)
table(dat12b$exerany2, useNA = "always") 
summary(dat12b$exerany2)

#missing
```

#CHD
```{r}
class(dat12b$cvdcrhd4)
table(dat12b$cvdcrhd4, useNA = "always") 
summary(dat12b$cvdcrhd4)

#missing
```


#health coverage
```{r}
class(dat12b$hlthpln1)
table(dat12b$hlthpln1, useNA = "always") 
summary(dat12b$hlthpln1)

#missing
```

#Recoding variables#

```{r}
#sex
dat12b$sex <- as.factor(dat12b$sex)

table(dat12b$sex, useNA = "always")

dat12b$sex1 <- car::Recode(dat12b$sex, recodes = "1='Male'; 2='Female'; else=NA",
                      levels = c('Male', 'Female'), as.factor=T)

table(dat12b$sex1, useNA = "always")

```

#recoding 7 and 9 to NA of AGE 
```{r}
table(dat12b$age, useNA = "always")

dat12b$age1 <- ifelse(dat12b$age == 7 | dat12b$age == 9, NA, dat12b$age)

table(dat12b$age1, useNA = "always")
```

#centering age
```{r}
dat12b$ageC <- dat12b$age1 - 18

summary(dat12b$ageC)
table(dat12b$ageC, useNA = "always")
```

#Categorizing AGE
```{r}
dat12b$age2 <- as.factor(dat12b$age1)

table(dat12b$age2, useNA = "always")

dat12b$ageF <- recode(dat12b$age2,
  "18:24='18-24'; 25:34='25-34'; 35:44='35-44'; 45:54='45-54'; 55:64='55-64' ; 65:99='65+'; else=NA")

table(dat12b$ageF, useNA = "always")
```


```{r}
#race
dat12b$racegr2 <- as.factor(dat12b$racegr2)

table(dat12b$racegr2, useNA = "always")

dat12b$race1 <- car::Recode(dat12b$racegr2, recodes = "1='Non-Hispanic White'; 2='Non-Hispanic Black'; 3='Non-Hispanic Other race'; 4='Non-Hispanic Multiracial'; 5='Hispanic'; else=NA",
                      levels = c('Non-Hispanic White', 'Non-Hispanic Black', 'Non-Hispanic Other race', 'Non-Hispanic Multiracial', 'Hispanic'), as.factor=T)

table(dat12b$race1, useNA = "always")
```


```{r}
#marital status
dat12b$marital <- as.factor(dat12b$marital)

table(dat12b$marital, useNA = "always")

dat12b$marital1 <- car::Recode(dat12b$marital, recodes = "1='Married'; 2='Divorced'; 3='Widowed'; 4='Separated'; 5='Never married'; 6='A member of an unmarried couple'; else=NA",
                      levels = c('Married', 'Divorced', 'Widowed', 'Separated', 'Never married', 'A member of an unmarried couple'), as.factor=T)

table(dat12b$marital1, useNA = "always")
```

```{r}
#education
dat12b$educa <- as.factor(dat12b$educa)

table(dat12b$educa, useNA = "always")

# dat12b$educa1 <- car::Recode(dat12b$educa, recodes = "1='Never attended'; 2='Elementary'; 3='Some high school'; 4='High school gaduate'; 5='Some college or technical school'; 6='College graduate'; else=NA",
#                       levels = c('Never attended', 'Elementary', 'Some high school', 'High school gaduate', 'Some college or technical school', 'College graduate'), as.factor=T)
                       
dat12b$educa1 <- car::Recode(dat12b$educa, recodes = "1:2='Less than high school'; 3:4='High school'; 5='Some college'; 6='College graduate'; else=NA", 
                             levels = c('Less than high school', 'High school', 'Some college', 'College graduate'), as.factor=T)

table(dat12b$educa1, useNA = "always")
```

```{r}
#employment
dat12b$employ1 <- as.factor(dat12b$employ)

table(dat12b$employ, useNA = "always")

dat12b$employ1 <- car::Recode(dat12b$employ, recodes = "1='Employed for wages'; 2='Self-employed'; 3='Out of work for more than 1 year'; 4='Out of work for less that 1 year'; 5='Homemaker'; 6='Student'; 7='Retired'; 8='Unable to work'; else=NA",
                      levels = c('Employed for wages', 'Self-employed', 'Out of work for more than 1 year', 'Out of work for less that 1 year', 'Homemaker', 'Student', 'Retired', 'Unable to work'), as.factor=T)

table(dat12b$employ1, useNA = "always")
```

```{r}
#general health
# dat12b$genhlth1 <- as.factor(dat12b$genhlth)
# 
# table(dat12b$genhlth, useNA = "always")
# 
# dat12b$genhlth1 <- Recode(dat12b$genhlth, recodes = "1='Excellent'; 2='Very good'; 3='Good'; 4='Fair'; 5='Poor'; else=NA",
#                       levels = c('Excellent', 'Very good', 'Good', 'Fair', 'Poor'), as.factor=T)
# 
# table(dat12b$genhlth1, useNA = "always")
```

```{r}
# #general health
dat12b$genhlth <- as.factor(dat12b$genhlth)

table(dat12b$genhlth, useNA = "always")

# dat12b <- mutate(dat12b, genhlth1 = ifelse(genhlth %in% c(1, 2), "Excellent",
#                                      ifelse(genhlth %in% c(3, 4, 5), "Poor", NA)))
#
dat12b$genhlth1 <- car::Recode(dat12b$genhlth, recodes = "1:2='Excellent/Very good'; 3:5='Good/Fair/Poor'; else=NA", as.factor=T)

table(dat12b$genhlth1, useNA = "always")
```

```{r}
dat12b$genhlth2 <- car::Recode(dat12b$genhlth1, recodes="'Excellent/Very good'=0; 'Good/Fair/Poor'=1")
 
table(dat12b$genhlth2, useNA = "always")
```


```{r}
#having depression 
dat12b$addepev2a <- as.factor(dat12b$addepev2)

table(dat12b$addepev2, useNA = "always")

dat12b$depr1 <- car::Recode(dat12b$addepev2, recodes = "1='Yes'; 2='No'; else=NA",
                      levels = c('Yes', 'No'), as.factor=T)

table(dat12b$depr1, useNA = "always")
```


```{r}
#having depression 

table(dat12b$addepev2, useNA = "always")

dat12b$depr1 <- car::Recode(dat12b$addepev2, recodes = "1='Yes'; 2='No'; else=NA",
                      levels = c('Yes', 'No'), as.factor=T)

table(dat12b$depr1, useNA = "always")
```

```{r}
#exercise 
dat12b$exerany2 <- as.factor(dat12b$exerany2)

table(dat12b$exerany2, useNA = "always")

dat12b$exer1 <- car::Recode(dat12b$exerany2, recodes = "1='Yes'; 2='No'; else=NA",
                      levels = c('Yes', 'No'), as.factor=T)

table(dat12b$exer1, useNA = "always")
```


```{r}
#CVD 
dat12b$cvdcrhd4 <- as.factor(dat12b$cvdcrhd4)

table(dat12b$cvdcrhd4, useNA = "always")

dat12b$cvd1 <- car::Recode(dat12b$cvdcrhd4, recodes = "1='Yes'; 2='No'; else=NA",
                      levels = c('Yes', 'No'), as.factor=T)

table(dat12b$cvd1, useNA = "always")
```


```{r}
#health care access 
dat12b$hlthpln1 <- as.factor(dat12b$hlthpln1)

table(dat12b$hlthpln1, useNA = "always")

dat12b$hlthcov1 <- car::Recode(dat12b$hlthpln1, recodes = "1='Yes'; 2='No'; else=NA",
                      levels = c('Yes', 'No'), as.factor=T)

table(dat12b$hlthcov1, useNA = "always")
```


#creating a dataframe with only complete cases
#selecting variables for the final dataframe
```{r}
dat12c <- dat12b %>% 
  dplyr::select(intvid, seqno, iday, imonth, iyear, dispcode, psu, llcpwt, ststr, geostr, wt2, strwt, state, sex1, age1, ageC, ageF, race1,  marital1, educa1, employ1, genhlth1, genhlth2, depr1, exer1, cvd1, hlthcov1)%>%   
  filter(complete.cases(.))
```


#Calculating workload
```{r}
library(dplyr)

# Assuming dat12c is your original data frame
workload <- dat12c %>% 
   group_by(intvid) %>% 
   summarise(workload = n())



# Merge the summarization result back to the original data frame
dat12c <- left_join(dat12c, workload, by = "intvid")

# Print the resulting data frame
print(dat12c)
```

#Creating categories of workload from low to high using k-means (WILL USE THIS)
```{r}
#k-Means Clustering:
# Advantage: Groups data based on similarity in value, which can reveal natural groupings or patterns in the data that aren't based on percentiles. It's a form of unsupervised classification.
# Use Case: Effective when there are natural clusters in the data, and you want the categories to reflect these distinct groupings.

set.seed(123) # for reproducibility
clusters <- kmeans(dat12c$workload, centers = 4)
dat12c$wkl <- as.factor(clusters$cluster)

table(dat12c$wkl)

dat12c$wkl <- factor(dat12c$wkl, levels = c(1, 4, 2, 3), labels = c("Low", "Medium", "High", "Very high"))

table(dat12c$wkl)
```


```{r}
save(dat12c, file = "C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\dat12c.RData")
```

```{r}
load("C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\dat12c.RData")

names(dat12c)
```

#selecting sample of 30%
```{r}
set.seed(1220)
dat12c_hd <- dat12c %>%
                sample_frac(0.50, replace = FALSE)
```

```{r}
options(survey.adjust.domain.lonely=TRUE)
options(survey.lonely.psu="adjust")

#des <- svydesign(ids=~psu, strata = ~ststr, weights = ~wt2, data=dat12c_hd, nest = T)
```

```{r}
#Standardizing the cohesion score
dat12c_hd$wt3 <- scale(dat12c_hd$wt2, center = T, scale = T)

dat12c_hd$wt4 <- ifelse(dat12c_hd$wt3>0, dat12c_hd$wt3,0)
```


# Calculating the average number of interviewers per workload category
```{r}
avg <- dat12c_hd %>% 
   group_by(wkl) %>% 
   summarise(avg_interviews = mean(intvid), group = n())%>%
  mutate(percentage = (group / sum(group)) * 100)
avg
```

Average number of interviews conducted by Low (5,330) workload interviewers is 131.
Average number of interviews conducted by Medium (20,491) workload interviewers is 458.
Average number of interviews conducted by High (52,367) workload interviewers is 1,473.
Average number of interviews conducted by Very high (102,386) workload interviewers is 15,613.

```{r}
names(dat12c_hd)
table(dat12c_hd$wkl)
```

```{r}
# Group the data by the workload group (wkl) and calculate workload statistics
workload_stats <- dat12c_hd %>%
  group_by(wkl) %>%
  summarise(
    min_workload = min(intvid),  # Minimum number of interviews within the workload group
    max_workload = max(intvid),  # Maximum number of interviews within the workload group
    mean_workload = mean(intvid),  # Mean number of interviews within the workload group
    median_workload = median(intvid)  # Median number of interviews within the workload group
  )
workload_stats
```


```{r}
# Assuming your data is stored in a data.frame named 'data'

# Count the number of unique interviewer IDs
# length(unique(dat12c_lowWL$intvid))
# length(unique(dat12c_MedWL$intvid))
# length(unique(dat12c_HWL$intvid))
# length(unique(dat12c_VHWL$intvid))
# length(unique(dat12c_hd$intvid))
# length(unique(dat12c$intvid))
# 
# # Assuming your data is stored in a data.frame named 'data'
# 
# # Filter data for interviewer ID 123
# filtered_data <- dat12c_lowWL[dat12c_lowWL$intvid == 123, ]
# 
# # Sum the number of interviews
# total_interviews <- nrow(filtered_data)
# 
# # Print the result
# cat("Total interviews conducted by interviewer ID 123:", total_interviews)

```


```{r}
# workload_by_interviewer <- dat12c_hd %>% 
#    group_by(intvid, wkl) %>% 
#    summarise(total_interviews = sum(intvid))
# 
# # View the resulting dataframe
# workload_by_interviewer
```

```{r}
# Group by interviewer and workload level, then summarize the range of interviews
# workload_range_by_interviewer <- dat12c_hd %>% 
#    group_by(intvid, wkl) %>% 
#    summarise(min_interviews = min(intvid),
#              max_interviews = max(intvid))
# 
# # View the resulting dataframe
# workload_range_by_interviewer

```


```{r}
# noint1 <-  dat12c_hd %>% 
#    group_by(wkl) %>% 
#    summarise(group = n())%>%
#   mutate(percentage = (group / sum(intvid)) * 100)
#    
# noint1
```


```{r}
# noint1 <- dat12c_hd %>% 
#    group_by(wkl, intvid) %>% 
#    summarise(num_interviews = n()) %>%
#    group_by(wkl) %>%
#    summarise(min_interviews = min(num_interviews),
#              max_interviews = max(num_interviews))
# 
# noint1
```

```{r}
# length(unique(dat12$intvid))
# dat12$r <- unique(dat12$intvid)
# r
```


```{r}
# r <- tbl_cross(dat12, row = intvid, col = state)
# r
```

#finding number of interviewers in the full data
```{r}
# Assuming your data frame is called 'your_data', you can count unique combinations of INTVID and _state variables like this:
unique_counts <- dat12 %>% 
  group_by(intvid, state) %>% 
  summarise(count = n())

# Count the number of unique interviewers
num_unique_interviewers <- nrow(unique_counts)
num_unique_interviewers
```
16,968



```{r}
unique_counts1 <- dat12c %>% 
  group_by(intvid, state) %>% 
  summarise(count = n())

# Count the number of unique interviewers
num_unique_interviewers <- nrow(unique_counts)
num_unique_interviewers


# Merge the summarization result back to the original data frame
dat12c <- left_join(dat12c, unique_counts1, by = "intvid")

# Print the resulting data frame
print(dat12c)
```

#Creating categories of workload from low to high using k-means (WILL USE THIS)
```{r}
#k-Means Clustering:
# Advantage: Groups data based on similarity in value, which can reveal natural groupings or patterns in the data that aren't based on percentiles. It's a form of unsupervised classification.
# Use Case: Effective when there are natural clusters in the data, and you want the categories to reflect these distinct groupings.

set.seed(123) # for reproducibility
clusters <- kmeans(dat12c$workload, centers = 4)
dat12c$wkl <- as.factor(clusters$cluster)

table(dat12c$wkl)

dat12c$wkl <- factor(dat12c$wkl, levels = c(1, 4, 2, 3), labels = c("Low", "Medium", "High", "Very high"))

table(dat12c$wkl)
```

#number of interviewers in 50% data
```{r}
unique_counts50 <- dat12c_hd %>% 
  group_by(intvid, state) %>% 
  summarise(count = n())

# Count the number of unique interviewers
num_unique_interviewer50 <- nrow(unique_counts50)
num_unique_interviewer50
```
10124

#number of interviewers for low workload
```{r}
unique_countsL <- dat12c_lowWL %>% 
  group_by(intvid, state) %>% 
  summarise(count = n())

# Count the number of unique interviewers
num_unique_interviewersL <- nrow(unique_countsL)
num_unique_interviewersL
```
99

#number of interviewers for Medium workload
```{r}
unique_countsM <- dat12c_MedWL %>% 
  group_by(intvid, state) %>% 
  summarise(count = n())

# Count the number of unique interviewers
num_unique_interviewersM <- nrow(unique_countsM)
num_unique_interviewersM
```
434

#number of interviewers for High workload
```{r}
unique_countsH <- dat12c_HWL %>% 
  group_by(intvid, state) %>% 
  summarise(count = n())

# Count the number of unique interviewers
num_unique_interviewersH <- nrow(unique_countsH)
num_unique_interviewersH
```
1438

#number of interviewers for VH workload
```{r}
unique_countsVH <- dat12c_VHWL %>% 
  group_by(intvid, state) %>% 
  summarise(count = n())

# Count the number of unique interviewers
num_unique_interviewersVH <- nrow(unique_countsVH)
num_unique_interviewersVH
```
8153


```{r}
# Group the data by INTVID and count the number of interviews for each interviewer
workload <- your_data %>%
  group_by(INTVID) %>%
  summarise(num_interviews = n())

# Summary statistics of workload
summary_stats <- summary(workload$num_interviews)

# Show summary statistics
print(summary_stats)

# You can also find the range of interviews
range_workload <- range(workload$num_interviews)

# Show the range of interviews
print(range_workload)

```


#Descriptives table
```{r}
var_label(dat12c_hd) <- list(
                      sex1 = "Sex of Respondent",
                      ageF = "Age",
                      race1 = "Race and Ethnicity",
                      marital1 = "Marital Status",
                      educa1 = "Educational Attainment",
                      employ1 = "Employment Status",
                      genhlth2 = "Self-rated General Health",
                      depnew1 = "Having any Depression",
                      exernew = "Any Exercise",
                      hcovnew = "Any Health Coverage")
```


**Descriptives table**
```{r Sample characteristics, warning=FALSE, message=FALSE}
set_gtsummary_theme(theme_gtsummary_compact(set_theme = TRUE))

#To get the descriptives
des1 <- 
  survey::svydesign(ids=~psu, strata = ~ststr, weights = ~llcpwt, data=dat12c_hd, nest = T) %>%
      tbl_svysummary(
              include = c(sex1, ageF, race1, marital1, educa1, employ1, genhlth2, depnew1, exernew, hcovnew),
              type = list(all_dichotomous() ~ "categorical",
                          all_continuous() ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean} ({sd})",
                          all_categorical() ~ "{p}"),
              percent = "column",
              digits = all_continuous() ~ 1) %>%
  bold_labels() %>%
  italicize_levels() %>% 
  as_flex_table()

des1
```

```{r}
save_as_docx(des1, path = "C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\Des table 1.docx")
```


############################## Modeling Approach ##########################################

```{r}
#dat12c_hd$wt2a <- scale(dat12c_hd$wt2, center = T, scale = T)
```


#LRT function
```{r, echo=TRUE}
# Function to calculate LRT p-values for variances of random effects
lrt.pvalue <- function(fit1, fit2) {
  lrtstat <-
    (-2 * as.numeric(logLik(fit2))) - (-2*as.numeric(summary(fit1)$logLik))
  pvalue = 0.5 * (1 - pchisq(lrtstat, 2)) + 0.5 * (1 - pchisq(lrtstat, 1))
  return(pvalue)
}
```


#with general health

#FOR LOW WORKLOAD
```{r}
dat12c_lowWL <- dat12c_hd %>%
            filter(wkl=="Low")

```

```{r}
modgen1Low <- glmer(genhlth2 ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_lowWL)

summary(modgen1Low)
#intercept not sig
```

#icc for Low
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance1 <- VarCorr(modgen1Low)$intvid[1]

# Calculate ICC
icc1 <- random_intercept_variance1 / (random_intercept_variance1 + pi^2 / 3)
icc1
#0.03
```


#FOR MEDIUM WORKLOAD
```{r}
dat12c_MedWL <- dat12c_hd %>%
            filter(wkl=="Medium")

```

```{r}
modgen1Med <- glmer(genhlth2 ~ 1 + (1 | intvid),
                    weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_MedWL)

summary(modgen1Med)
#intercept sig
```

#icc for MEDIUM
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance2 <- VarCorr(modgen1Med)$intvid[1]

# Calculate ICC
icc2 <- random_intercept_variance2 / (random_intercept_variance2 + pi^2 / 3)
icc2
#0.05
```

#FOR HIGH WORKLOAD
```{r}
dat12c_HWL <- dat12c_hd %>%
            filter(wkl=="High")

```

```{r}
modgen1H <- glmer(genhlth2 ~ 1 + (1 | intvid),
                  weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_HWL)

summary(modgen1H)
#intercept sig
```

#icc for HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance3 <- VarCorr(modgen1H)$intvid[1]

# Calculate ICC
icc3 <- random_intercept_variance3 / (random_intercept_variance3 + pi^2 / 3)
icc3
#0.04
```


#FOR VERY HIGH WORKLOAD
```{r}
dat12c_VHWL <- dat12c_hd %>%
            filter(wkl=="Very high")

```

```{r}
modgen1VH <- glmer(genhlth2 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_VHWL)

summary(modgen1VH)
#intercept sig
```

#icc for VERY HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance4 <- VarCorr(modgen1VH)$intvid[1]

# Calculate ICC
icc4 <- random_intercept_variance4 / (random_intercept_variance4 + pi^2 / 3)
icc4
#0.01
```

*ICC decreases

#fitting a model with random intercept only
```{r}
modgen1 <- glmer(genhlth2 ~ sex1 + ageF + race1 + (1 | intvid),
                 weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(modgen1)
#int var 0.3559

```

```{r}
modgen1a <- glm(genhlth2 ~ sex1 + ageF + race1,
                  weights = wt4,
                  family = binomial(link = "logit"),
                data = dat12c_hd)

summary(modgen1a)
```


#Test the null hypothesis that the variance of the random intercepts is equal to zero

#LRT test for Random intercept
```{r}
lrt.pvalue(modgen1, modgen1a)

#0: P<0.05
#We would reject the null hypothesis given the very small p-value, and conclude that the variance of the random intercepts is definitely greater than zero.
```


#fitting a model adding workload as a predictor
```{r}
modgen2 <- glmer(genhlth2 ~ wkl + (1 | intvid),
                 weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(modgen2)
#Workload not significant
#correlation high
#RI=0.3875
```

```{r}
genred <- tbl_regression(modgen2, exp = T) %>% 
  bold_p()

genred
```

```{r}
# save_as_docx(genred, path = "C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\genred.docx")
```

#percentage of the variance in the random intercepts is explained by workload
```{r}
#Extracting variance from random intercepts
var1 <- VarCorr(modgen1)$intvid[1,1]  
var1

var2 <- VarCorr(modgen2)$intvid[1,1]  
var2

#Compute the reduction in variance:
reduction_in_variance <- (var2 - var1) / var1
reduction_in_variance*100

#8.87% variance due to the intercept
```

#adding predictors to explain variance in intercept
```{r}
modgen3 <- glmer(genhlth2 ~ sex1 + ageF + race1 + marital1 + educa1 + employ1 + wkl + (1 | intvid),
                 weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(modgen3)
#workload not significant
#RI variance=0.3954
```

```{r}
genfull <- tbl_regression(modgen3, exp = T) %>% 
  bold_p()

genfull
```

```{r}
save_as_docx(genfull, path = "C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\Gentable.docx")
```

```{r}
library(lmtest)
lrtest(modgen3, modgen2)
anova(modgen3, modgen2)
#significant
```

```{r}
tbl_merge_ex3 <-
  tbl_merge( #Table merge function
    tbls = list(genred, genfull), # Selecting the tables to be included in the combined table output 
    # More objects can be added here
    tab_spanner = c("**Reduced model**", "**Full model**") # Naming the models
  ) %>% 
  bold_labels()%>% 
  italicize_levels()%>% 
  as_flex_table() #gtsummary packages can crete objects as gt, flextable or huxtable, and many more. These are useful pacakges to further formatting tables according to presentation and publication needs.
tbl_merge_ex3
```

```{r}
save_as_docx(tbl_merge_ex3, path = "C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\gentable.docx")
```


```{r}
AIC(modgen2, modgen3) #modgen3 has the lowest AIC
BIC(modgen2, modgen3) #modgen3 has the lowest AIC
```

#Model diagnostic

#modgen3
```{r}
# compute predicted probability
dat12c_hd$predicted_prob <- predict(modgen3, newdata = dat12c_hd, type = "response")

# Combine predicted probabilities with the original dataset
result <- data.frame(dat12c_hd$genhlth2, Predicted_Prob = dat12c_hd$predicted_prob)
```

```{r}
# create plot of predicted result 
ggplot(result, aes(x = dat12c_hd$genhlth2, y = Predicted_Prob), weights=dat12c_hd$wt4) +
        geom_boxplot(fill = "lightblue", color = "blue") +
        labs(x = "Self-rated general health for modgen3", y = "Predicted Probability")

#there is a difference in the side by side boxplots 
```

#Binned residual plot
```{r}
library(arm)
dat12c_hd$phat<-predict(modgen3,type="response")
dat12c_hd$resid<-resid(modgen3,type="response")

binnedplot(dat12c_hd$phat,dat12c_hd$resid)
```

#Plot of the EBLUPS for the random intercept
```{r}
qqnorm(ranef(modgen3)$intvid[,1]) 
qqline(ranef(modgen3)$intvid[,1])
```

#AUC
```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE, fig.show='hide'}
#trying a different way to plot AUC with value
library(ROCR)

# Create prediction object
m1.prediction <- prediction(dat12c_hd$phat, dat12c_hd$genhlth2)

# Calculate AUC value
m1.auc <- performance(m1.prediction, "auc")@y.values[[1]]
m1.auc

# Plot ROC curve
m1.perf <- performance(m1.prediction, "tpr", "fpr")
plot(m1.perf, main = "ROC Curve", col = "blue", lwd = 2)
abline(a = 0, b = 1, lty = 2, lwd = 2)
legend("bottomright", legend = paste("AUC = ", round(m1.auc, 2)), col = "blue", lwd = 2, bty = "n")

#71%
```

############################################################

#WITH DEPRESSION

```{r}
table(dat12c_hd$depr1, useNA = "always")

dat12c_hd$depnew1 <- car::Recode(dat12c_hd$depr1, recodes="'No'=0; 'Yes'=1")
 
table(dat12c_hd$depnew1, useNA = "always")
```

#FOR LOW WORKLOAD
```{r}
moddep1Low <- glmer(depr1 ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_lowWL)

summary(moddep1Low)
#sig
#
#
moddep1LowN <- glmer(depnew1 ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_lowWL)

summary(moddep1LowN)
```

#icc for Low
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance1 <- VarCorr(moddep1Low)$intvid[1]

# Calculate ICC
icc1 <- random_intercept_variance1 / (random_intercept_variance1 + pi^2 / 3)
icc1
#0.00
#
random_intercept_variance1N <- VarCorr(moddep1LowN)$intvid[1]

# Calculate ICC
icc1N <- random_intercept_variance1N / (random_intercept_variance1N + pi^2 / 3)
icc1N
#0.0003551129
```

#FOR MEDIUM WORKLOAD
```{r}
moddep1Med <- glmer(depr1 ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_MedWL)

summary(moddep1Med)
#sig

moddep1MedN <- glmer(depnew1 ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_MedWL)

summary(moddep1MedN)
```

#icc for MEDIUM
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance2 <- VarCorr(moddep1Med)$intvid[1]

# Calculate ICC
icc2 <- random_intercept_variance2 / (random_intercept_variance2 + pi^2 / 3)
icc2
#0.01
#
#
# Extract variance of the random intercept from the model
random_intercept_variance2N <- VarCorr(moddep1MedN)$intvid[1]

# Calculate ICC
icc2N <- random_intercept_variance2N / (random_intercept_variance2N + pi^2 / 3)
icc2N
#0.00875236
```

#FOR HIGH WORKLOAD
```{r}
moddep1H <- glmer(depr1 ~ 1 + (1 | intvid),
                  weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_HWL)

summary(moddep1H)
#intercept sig

moddep1HN <- glmer(depnew1 ~ 1 + (1 | intvid),
                  weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_HWL)

summary(moddep1HN)
```

#icc for HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance3 <- VarCorr(moddep1H)$intvid[1]

# Calculate ICC
icc3 <- random_intercept_variance3 / (random_intercept_variance3 + pi^2 / 3)
icc3
#0.01

random_intercept_variance3N <- VarCorr(moddep1HN)$intvid[1]

# Calculate ICC
icc3N <- random_intercept_variance3N / (random_intercept_variance3N + pi^2 / 3)
icc3N
#0.007483209
```


#FOR VERY HIGH WORKLOAD
```{r}
moddep1VH <- glmer(depr1 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_VHWL)

summary(moddep1VH)
#intercept sig
#
#
moddep1VHN <- glmer(depnew1 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_VHWL)

summary(moddep1VHN)
```

#icc for VERY HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance4 <- VarCorr(moddep1VH)$intvid[1]

# Calculate ICC
icc4 <- random_intercept_variance4 / (random_intercept_variance4 + pi^2 / 3)
icc4
#0.02
#
random_intercept_variance4N <- VarCorr(moddep1VHN)$intvid[1]

# Calculate ICC
icc4N <- random_intercept_variance4N / (random_intercept_variance4N + pi^2 / 3)
icc4N
#0.0182969
```

*Slight increase

#fitting a model with random intercept and random slope and FE of workload
```{r}
deprmod1N <- glmer(depnew1 ~ sex1 + ageF + race1 + (1 | intvid),
                  weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(deprmod1N) 
#RI var=0.4426
```

```{r}
deprmod1aN <- glm(depnew1 ~ sex1 + ageF + race1,
                  weights = wt4,
                  family = binomial(link = "logit"),
                 data = dat12c_hd)

summary(deprmod1aN) 
#significant
```

```{r}
lrt.pvalue(deprmod1N, deprmod1aN)
#significant
```

#fitting a model taking out random slope
```{r}
deprmod2N <- glmer(depnew1 ~ wkl + (1 | intvid),
                  weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(deprmod2N)
#none significant
#RI var=0.4338
#high correlation
```

```{r}
depredN <- tbl_regression(deprmod2N, exp = T) %>% 
  bold_p()

depredN
```

```{r}
save_as_docx(depredN, path = "C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\depredN.docx")
```


#LRT test
```{r}
lrt.pvalue(deprmod1N, deprmod2N)
#significant
```

#percentage of the variance in the random intercepts is explained by workload
```{r}
#Extracting variance from random intercepts
var1N <- VarCorr(deprmod1N)$intvid[1,1]  
var1N

var2N <- VarCorr(deprmod2N)$intvid[1,1]  
var2N

#Compute the reduction in variance:
reduction_in_varianceN <- (var1N - var2N) / var1N
reduction_in_varianceN*100

#1.97% variance due to the intercept
```


#adding predictors to explain variance in intercept
```{r}
deprmod3N <- glmer(depnew1 ~ sex1 + ageF + race1 + marital1 + educa1 + employ1 + wkl + (1 | intvid),
  weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(deprmod3N)
#wkl not significant
#RI var=0.893
```


```{r}
depfullN <- tbl_regression(deprmod3N, exp = T) %>% 
  bold_p()

depfullN
```

```{r}
save_as_docx(depfullN, path = "C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\depfullN.docx")
```

```{r}
tbl_merge_ex4 <-
  tbl_merge( #Table merge function
    tbls = list(depredN, depfullN), # Selecting the tables to be included in the combined table output 
    # More objects can be added here
    tab_spanner = c("**Reduced model**", "**Full model**") # Naming the models
  ) %>% 
  bold_labels()%>% 
  italicize_levels()%>% 
  as_flex_table() #gtsummary packages can crete objects as gt, flextable or huxtable, and many more. These are useful pacakges to further formatting tables according to presentation and publication needs.

#as_gt() 

tbl_merge_ex4
```

```{r}
save_as_docx(tbl_merge_ex4, path = "C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\deptableN.docx")
```


```{r}
table(dat12c_hd$depr1, useNA = "always")

dat12c_hd$depnew1 <- car::Recode(dat12c_hd$depr1, recodes="'No'=0; 'Yes'=1")
 
table(dat12c_hd$depnew1, useNA = "always")
```

```{r}
deprmod4 <- glmer(depnew1 ~ sex1 + ageF + race1 + marital1 + educa1 + employ1 + wkl + (1 | intvid),
  weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(deprmod4)
#wkl not significant
#RI var=0.893
```

```{r}
depfull1 <- tbl_regression(deprmod4, exp = T) %>% 
  bold_p()

depfull1
```

```{r}
AIC(deprmod2, deprmod3) #deprmod3 has the lowest AIC
BIC(deprmod2, deprmod3) #deprmod3 has the lowest AIC
```


#Model diagnostic
```{r}
# compute predicted probability
dat12c_hd$predicted_prob <- predict(deprmod3, newdata = dat12c_hd, type = "response")

# Combine predicted probabilities with the original dataset
result <- data.frame(dat12c_hd$depr1, Predicted_Prob = dat12c_hd$predicted_prob)
```

```{r}
# create plot of predicted result 
ggplot(result, aes(x = dat12c_hd$depr1, y = Predicted_Prob), weights=dat12c_hd$wt4) +
        geom_boxplot(fill = "lightblue", color = "blue") +
        labs(x = "Having depression for modgen3", y = "Predicted Probability")

#there is a difference in the side by side boxplots 
```


#Plot of the EBLUPS for the random intercept
```{r}
qqnorm(ranef(deprmod3)$intvid[,1]) 
qqline(ranef(deprmod3)$intvid[,1])
```

#Binned residual plot
```{r}
library(arm)
dat12c_hd$phat<-predict(deprmod3,type="response")
dat12c_hd$resid<-resid(deprmod3,type="response")

binnedplot(dat12c_hd$phat,dat12c_hd$resid)
```

#AUC
```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE, fig.show='hide'}
#trying a different way to plot AUC with value
library(ROCR)

# Create prediction object
m1.prediction <- prediction(dat12c_hd$phat, dat12c_hd$depr1)

# Calculate AUC value
m1.auc <- performance(m1.prediction, "auc")@y.values[[1]]
m1.auc

# Plot ROC curve
m1.perf <- performance(m1.prediction, "tpr", "fpr")
plot(m1.perf, main = "ROC Curve", col = "blue", lwd = 2)
abline(a = 0, b = 1, lty = 2, lwd = 2)
legend("bottomright", legend = paste("AUC = ", round(m1.auc, 2)), col = "blue", lwd = 2, bty = "n")

#32%
```

```{r}
# Cigarette.Study$Cig.Plus.1 <- Cigarettes+1
# Cigarette.Study$Cig.Log <- log10(Cigarette.Study$Cig.Plus.1)
# dat12c_hd$depr1.1 <- dat12c_hd$depr1+1
```


***********************************************************************

#WITH EXERCISE

```{r}
table(dat12c_hd$exer1, useNA = "always")

dat12c_hd$exernew <- car::Recode(dat12c_hd$exer1, recodes="'No'=0; 'Yes'=1")
 
table(dat12c_hd$exernew, useNA = "always")
```


#FOR LOW WORKLOAD
```{r}
modex1Low <- glmer(exer1 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_lowWL)

summary(modex1Low)
#sign
#
modex1LowN <- glmer(exernew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_lowWL)

summary(modex1LowN)
```

#icc for Low
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance1 <- VarCorr(modex1Low)$intvid[1]

# Calculate ICC
icc1 <- random_intercept_variance1 / (random_intercept_variance1 + pi^2 / 3)
icc1
#0.04
#
random_intercept_variance1N <- VarCorr(modex1LowN)$intvid[1]

# Calculate ICC
icc1N <- random_intercept_variance1N / (random_intercept_variance1N + pi^2 / 3)
icc1N
#0.03802737
```

#FOR MEDIUM WORKLOAD
```{r}
modex1Med <- glmer(exer1 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_MedWL)

summary(modex1Med)
#sign
#
modex1MedN <- glmer(exernew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_MedWL)

summary(modex1MedN)
```

#icc for MEDIUM
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance2 <- VarCorr(modex1Med)$intvid[1]

# Calculate ICC
icc2 <- random_intercept_variance2 / (random_intercept_variance2 + pi^2 / 3)
icc2
#0.04
#
#
random_intercept_variance2N <- VarCorr(modex1MedN)$intvid[1]

# Calculate ICC
icc2N <- random_intercept_variance2N / (random_intercept_variance2N + pi^2 / 3)
icc2N
#0.03567
```

#FOR HIGH WORKLOAD
```{r}
modex1H <- glmer(exer1 ~ 1 + (1 | intvid),
                 weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_HWL)

summary(modex1H)
#intercept sig
#
modex1HN <- glmer(exernew ~ 1 + (1 | intvid),
                 weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_HWL)

summary(modex1HN)
```

#icc for HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance3 <- VarCorr(modex1H)$intvid[1]

# Calculate ICC
icc3 <- random_intercept_variance3 / (random_intercept_variance3 + pi^2 / 3)
icc3
#0.03
#
random_intercept_variance3N <- VarCorr(modex1HN)$intvid[1]

# Calculate ICC
icc3N <- random_intercept_variance3N / (random_intercept_variance3N + pi^2 / 3)
icc3N
#0.02903089
```


#FOR VERY HIGH WORKLOAD
```{r}
modex1VH <- glmer(exer1 ~ 1 + (1 | intvid),
                  weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_VHWL)

summary(modex1VH)
#intercept sig

modex1VHN <- glmer(exernew ~ 1 + (1 | intvid),
                  weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_VHWL)

summary(modex1VHN)
```

#icc for VERY HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance4 <- VarCorr(modex1VH)$intvid[1]

# Calculate ICC
icc4 <- random_intercept_variance4 / (random_intercept_variance4 + pi^2 / 3)
icc4
#0.02
#
random_intercept_variance4N <- VarCorr(modex1VHN)$intvid[1]

# Calculate ICC
icc4N <- random_intercept_variance4N / (random_intercept_variance4N + pi^2 / 3)
icc4N
#0.02080422
```

*ICC decreasing


#fitting a model with random intercept and random slope and FE of workload
```{r}
exermod1N <- glmer(exernew ~  wkl + sex1 + ageF + race1 + (1 | intvid),
                  weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(exermod1N)
#int significant
#RI var=0.7894
```

```{r}
exermod1aN <- glm(exernew ~ wkl + sex1 + ageF + race1,
                  weights = wt4,
                  family = binomial(link = "logit"),
                 data = dat12c_hd)

summary(exermod1aN) 
```

```{r}
lrt.pvalue(exermod1N, exermod1aN)
#0: p<0.05
```

#fitting a model taking out random slope
```{r}
exermod2N <- glmer(exernew ~ wkl + (1 | intvid),
                  weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(exermod2N)
#wkl not significant
#RI var=0.4668 
```

```{r}
set_gtsummary_theme(theme_gtsummary_compact(set_theme = TRUE))
exerredN <-tbl_regression(exermod2N, exp = T)%>%
  bold_p()

exerredN
```

```{r}
save_as_docx(exerredN, path = "C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\exerredN.docx")
```


#LRT test
```{r}
lrt.pvalue(exermod1N, exermod2N)
#0
#sig
```

#percentage of the variance in the random intercepts is explained by workload
```{r}
#Extracting variance from random intercepts
var1N <- VarCorr(exermod1N)$intvid[1,1]  
var1N

var2N <- VarCorr(exermod2N)$intvid[1,1]  
var2N

#Compute the reduction in variance:
reduction_in_varianceN <- (var2N - var1N) / var1N
reduction_in_varianceN*100

#4.53% variance due to the intercept
#
#new % is 7.82
```

#adding predictors to explain variance in intercept
```{r}
#W/ workload as both FE and RE
exermod3N <- glmer(exernew ~ sex1 + ageF + race1 + marital1 + educa1 + employ1 + wkl
               + (1 | intvid),
               weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(exermod3N)
#wkl not sig
#RI var=0.8509
```

```{r}
lrt.pvalue(exermod2N, exermod3N)
#sig
```

```{r}
set_gtsummary_theme(theme_gtsummary_compact(set_theme = TRUE))
exerfullN <-tbl_regression(exermod3N, exp = T) %>% 
  bold_p() 

exerfullN
```

```{r}
save_as_docx(exerfullN, path = "C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\exerfullN.docx")
```

```{r}
tbl_merge_ex1 <-
  tbl_merge( #Table merge function
    tbls = list(exerredN, exerfullN), # Selecting the tables to be included in the combined table output 
    # More objects can be added here
    tab_spanner = c("**Reduced model**", "**Full model**") # Naming the models
  ) %>% 
  bold_labels()%>% 
  italicize_levels()%>% 
  as_flex_table() #gtsummary packages can crete objects as gt, flextable or huxtable, and many more. These are useful pacakges to further formatting tables according to presentation and publication needs.

#as_gt() 

tbl_merge_ex1
```

```{r}
save_as_docx(tbl_merge_ex1, path = "C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\exertableN.docx")
```

```{r}
AIC(exermod2N, exermod3N) #mod3 has the lowest AIC
BIC(exermod2N, exermod3N) #mod3 has the lowest AIC
```

#removing employment 
```{r}
exermod3a <- glmer(exer1 ~ sex1 + ageF + race1 + marital1 + educa1 + wkl
               + (1 | intvid),
               weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(exermod3a)
#33% AUC
```

#removing education and marital stat
```{r}
exermod3b <- glmer(exer1 ~ sex1 + ageF + race1 + wkl
               + (1 | intvid),
               weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(exermod3b)
#39%
```

#removing education and marital stat
```{r}
exermod3c <- glmer(exer1 ~ sex1 + ageF + wkl
               + (1 | intvid),
               weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(exermod3c)
#39%
```

#Model diagnostic
```{r}
# compute predicted probability
dat12c_hd$predicted_prob <- predict(exermod3N, newdata = dat12c_hd, type = "response")

# Combine predicted probabilities with the original dataset
result <- data.frame(dat12c_hd$exernew, Predicted_Prob = dat12c_hd$predicted_prob)

# Print the result
head(result)
```

```{r}
# create plot of predicted result 
ggplot(result, aes(x = dat12c_hd$exernew, y = Predicted_Prob), weights=dat12c_hd$wt4) +
        geom_boxplot(fill = "lightblue", color = "blue") +
        labs(x = "Doing exercise for exermod3", y = "Predicted Probability")

#there is a difference in the side by side boxplots 
```


#Plot of the EBLUPS for the random intercept
```{r}
qqnorm(ranef(exermod3N)$intvid[,1]) 
qqline(ranef(exermod3N)$intvid[,1])

# library(sjPlot)
# random_effects <- ranef(exermod3)
# sjp.efc(random_effects$intvid, sort.random = TRUE)


```

#Binned residual plot
```{r}
library(arm)
dat12c_hd$phat<-predict(exermod3N,type="response")
dat12c_hd$resid<-resid(exermod3N,type="response")

binnedplot(dat12c_hd$phat,dat12c_hd$resid)
```

#AUC
```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE, fig.show='hide'}
#trying a different way to plot AUC with value
library(ROCR)

# Create prediction object
m1.prediction <- prediction(dat12c_hd$phat, dat12c_hd$exer1)

# Calculate AUC value
m1.auc <- performance(m1.prediction, "auc")@y.values[[1]]
m1.auc

# Plot ROC curve
m1.perf <- performance(m1.prediction, "tpr", "fpr")
plot(m1.perf, main = "ROC Curve of Exercise", col = "blue", lwd = 2)
abline(a = 0, b = 1, lty = 2, lwd = 2)
legend("bottomright", legend = paste("AUC = ", round(m1.auc, 2)), col = "blue", lwd = 2, bty = "n")

#31%
```

```{r}
AIC(exermod1, exermod2) #mod3 has the lowest AIC
BIC(exermod2, exermod3) #mod3 has the lowest AIC
```


```{r}
# dat12c_hd$exer1s <- sqrt(dat12c_hd$exer1)
# Cigarette.Study$Cig.Log <- log10(Cigarette.Study$Cig.Plus.1)

```

```{r}
# plot(exermod3)
# 
# # Assuming your model is stored in 'my_model'
# predicted_probs <- predict(my_model, type = "response")
# 
# # Plot the distribution of predicted probabilities
# hist(dat12c_hd$phat, main = "Distribution of Predicted Probabilities", xlab = "Predicted Probabilities")

```

```{r}
# Assuming your model is stored in 'mixed_model'
eblups <- ranef(exermod3)$intvid

# Extract EBLUPs as a numeric vector
eblup_values <- as.numeric(unlist(eblups))

# Create a boxplot to visualize the distribution
plot(eblup_values, main = "Distribution of EBLUPs", ylab = "EBLUPs")
```





*******************************************************************************

#WITH CVD

#FOR LOW WORKLOAD
```{r}
modcvd1Low <- glmer(cvd1 ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_lowWL)

summary(modcvd1Low)

```

#icc for Low
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance1 <- VarCorr(modcvd1Low)$intvid[1]

# Calculate ICC
icc1 <- random_intercept_variance1 / (random_intercept_variance1 + pi^2 / 3)
icc1
#0.02
```

#FOR MEDIUM WORKLOAD
```{r}
modcvd1Med <- glmer(cvd1 ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_MedWL)

summary(modcvd1Med)
#sig
```

#icc for MEDIUM
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance2 <- VarCorr(modcvd1Med)$intvid[1]

# Calculate ICC
icc2 <- random_intercept_variance2 / (random_intercept_variance2 + pi^2 / 3)
icc2
#0.02
```

#FOR HIGH WORKLOAD
```{r}
modcvd1H <- glmer(cvd1 ~ 1 + (1 | intvid),
                  weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_HWL)

summary(modcvd1H)
#intercept sig
```

#icc for HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance3 <- VarCorr(modcvd1H)$intvid[1]

# Calculate ICC
icc3 <- random_intercept_variance3 / (random_intercept_variance3 + pi^2 / 3)
icc3
#0.06
```


#FOR VERY HIGH WORKLOAD
```{r}
modcvd1VH <- glmer(cvd1 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_VHWL)

summary(modcvd1VH)
#intercept sig
```

#icc for VERY HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance4 <- VarCorr(modcvd1VH)$intvid[1]

# Calculate ICC
icc4 <- random_intercept_variance4 / (random_intercept_variance4 + pi^2 / 3)
icc4
#0.09
```

#fitting a model with random intercept and random slope and FE of workload
```{r}
cvdmod1 <- glmer(cvd1 ~ wkl + sex1 + ageF + race1 + (1 | intvid),
                 weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(cvdmod1)
#int sig
#RI=1.717
```

```{r}
cvdmod1a <- glm(cvd1 ~ wkl + sex1 + ageF + race1,
                 weights = wt4,
                  family = binomial(link = "logit"),
                data = dat12c_hd)

summary(cvdmod1a) 
```

#LRT test
```{r}
lrt.pvalue(cvdmod1, cvdmod1a)
#0: P<0.05
```

#fitting a model taking out random slope
```{r}
cvdmod2 <- glmer(cvd1 ~ wkl + (1 | intvid),
                 weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(cvdmod2)
#wkl not sig
#RI var=1.687
```

#LRT test
```{r}
lrt.pvalue(cvdmod1, cvdmod2)
#0: P<0.05
```

#percentage of the variance in the random intercepts is explained by workload
```{r}
#Extracting variance from random intercepts
var1 <- VarCorr(cvdmod1)$intvid[1,1]  
var1

var2 <- VarCorr(cvdmod2)$intvid[1,1]  
var2

#Compute the reduction in variance:
reduction_in_variance <- (var1 - var2) / var1
reduction_in_variance*100

#1.75% variance due to the intercept
```


#adding predictors to explain variance in intercept

```{r}
#W/ workload as both FE and RE
cvdmod3 <- glmer(cvd1 ~ sex1 + ageF + race1 + marital1 + educa1 + employ1 + wkl + (1 | intvid),
                 weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(cvdmod3)
#WKl Med and VH marginally significant
#RI=1.882
```

```{r}
tbl_regression(cvdmod3, exp = T)
```

```{r}
lrt.pvalue(cvdmod3, cvdmod2)
#sig
```

```{r}
AIC(cvdmod2, cvdmod3) #mod3 has the lowest AIC
BIC(cvdmod2, cvdmod3) #mod3 has the lowest AIC
```


#Model diagnostic
#cvdmod3
```{r}
# compute predicted probability
dat12c_hd$predicted_prob <- predict(cvdmod3, newdata = dat12c_hd, type = "response")

# Combine predicted probabilities with the original dataset
result <- data.frame(dat12c_hd$cvd1, Predicted_Prob = dat12c_hd$predicted_prob)

# Print the result
head(result)
```

```{r}
# create plot of predicted result 
ggplot(result, aes(x = dat12c_hd$cvd1, y = Predicted_Prob), weights=dat12c_hd$wt4) +
        geom_boxplot(fill = "lightblue", color = "blue") +
        labs(x = "CVD for cvdmod3", y = "Predicted Probability")

#there is a difference in the side by side boxplots 
```


#Plot of the EBLUPS for the random intercept
```{r}
qqnorm(ranef(cvdmod3)$intvid[,1]) 
qqline(ranef(cvdmod3)$intvid[,1])
```

****************************************************

#FOR HEALTH COVERAGE

```{r}
table(dat12c_hd$hlthcov1, useNA = "always")

dat12c_hd$hcovnew <- car::Recode(dat12c_hd$hlthcov1, recodes="'No'=0; 'Yes'=1")
 
table(dat12c_hd$hcovnew, useNA = "always")
```

#FOR LOW WORKLOAD
```{r}
modhcovLowN <- glmer(hcovnew ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_lowWL)

summary(modhcovLowN)
```

#icc for Low
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance1N <- VarCorr(modhcovLowN)$intvid[1]

# Calculate ICC
icc1N <- random_intercept_variance1N / (random_intercept_variance1N + pi^2 / 3)
icc1N
#0.03
```

#FOR MEDIUM WORKLOAD
```{r}
modhcovMedN <- glmer(hcovnew ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_MedWL)

summary(modhcovMedN)

```

#icc for MEDIUM
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance2N <- VarCorr(modhcovMedN)$intvid[1]

# Calculate ICC
icc2N <- random_intercept_variance2N / (random_intercept_variance2N + pi^2 / 3)
icc2N
#0.02
```

#FOR HIGH WORKLOAD
```{r}
modhcovHN <- glmer(hcovnew ~ 1 + (1 | intvid),
                  weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_HWL)

summary(modhcovHN)
#intercept sig
```

#icc for HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance3N <- VarCorr(modhcovHN)$intvid[1]

# Calculate ICC
icc3N <- random_intercept_variance3N / (random_intercept_variance3N + pi^2 / 3)
icc3N
#0.05
#
#0.04495665 NEW
```


#FOR VERY HIGH WORKLOAD
```{r}
modhcovVHN <- glmer(hcovnew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_VHWL)

summary(modhcovVHN)
#intercept sig
```

#icc for VERY HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance4N <- VarCorr(modhcovVHN)$intvid[1]

# Calculate ICC
icc4N <- random_intercept_variance4N / (random_intercept_variance4N + pi^2 / 3)
icc4N
#0.08
```

*increase

#fitting a model with random intercept and random slope and FE of workload
```{r}
hcovmod1N <- glmer(hcovnew ~ wkl + sex1 + ageF + race1 + (1 | intvid),
                 weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(hcovmod1N)
#sig
```

```{r}
hcovmod1aN <- glm(hcovnew ~ wkl + sex1 + ageF + race1,
                 weights = wt4,
                  family = binomial(link = "logit"),
                 data = dat12c_hd)

summary(hcovmod1aN) 
```

#LRT test
```{r}
lrt.pvalue(hcovmod1N, hcovmod1aN)
#sig
```

#fitting a model taking out random slope
```{r}
hcovmod2N <- glmer(hcovnew ~ wkl + (1 | intvid),
                 weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(hcovmod2N)
#wkl not sig
#RI=1.357
#high corr
```

```{r}
hcovredN <-tbl_regression(hcovmod2N, exp = T) %>% 
  bold_p()

hcovredN
```

```{r}
save_as_docx(hcovredN, path = "C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\hcovredN.docx")
```


#LRT test
```{r}
lrt.pvalue(hcovmod1N, hcovmod2N)
#sig
```

#percentage of the variance in the random intercepts is explained by workload
```{r}
#Extracting variance from random intercepts
var1N <- VarCorr(hcovmod1N)$intvid[1,1]  
var1N

var2N <- VarCorr(hcovmod2N)$intvid[1,1]  
var2N

#Compute the reduction in variance:
reduction_in_varianceN <- (var2N - var1N) / var1
reduction_in_varianceN*100

#16.9% variance due to the intercept
```


#adding predictors to explain variance in intercept

```{r}
#W/ workload as both FE and RE
hcovmod3N <- glmer(hcovnew ~ sex1 + ageF + race1 + marital1 + educa1 + employ1 + wkl + (1 | intvid),
                 weights = wt4,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_hd)

summary(hcovmod3N)
#wkl not sign
#RI=1.284
```

```{r}
hcovfullN <-tbl_regression(hcovmod3N, exp = T) %>% 
  bold_p()

hcovfullN
```

```{r}
save_as_docx(hcovmod3N, path = "C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\hcovfullN.docx")
```

```{r}
tbl_merge_ex2 <-
  tbl_merge( #Table merge function
    tbls = list(hcovredN, hcovfullN), # Selecting the tables to be included in the combined table output 
    # More objects can be added here
    tab_spanner = c("**Reduced model**", "**Full model**") # Naming the models
  ) %>% 
  bold_labels()%>% 
  italicize_levels()%>% 
  as_flex_table() #gtsummary packages can crete objects as gt, flextable or huxtable, and many more. These are useful pacakges to further formatting tables according to presentation and publication needs.

#as_gt() 

tbl_merge_ex2
```

```{r}
save_as_docx(tbl_merge_ex2, path = "C:\\Users\\ilmul\\Documents\\UMICH\\Winter 2024\\721\\BRFSS12\\hcovtableN.docx")
```

```{r}
lrt.pvalue(hcovmod3, hcovmod2)
#sig
```

```{r}
AIC(hcovmod2, hcovmod3) #hcovmod3 has the lowest AIC
BIC(hcovmod2, hcovmod3) #hcovmod3 has the lowest AIC
```


#Model diagnostic

```{r}
# compute predicted probability
dat12c_hd$predicted_prob <- predict(hcovmod3, newdata = dat12c_hd, type = "response")

# Combine predicted probabilities with the original dataset
result <- data.frame(dat12c_hd$hlthcov1, Predicted_Prob = dat12c_hd$predicted_prob)

# Print the result
head(result)
```

```{r}
# create plot of predicted result 
ggplot(result, aes(x = dat12c_hd$hlthcov1, y = Predicted_Prob), weights=dat12c_hd$wt4) +
        geom_boxplot(fill = "lightblue", color = "blue") +
        labs(x = "Health coverage for hcovmod3", y = "Predicted Probability")

#there is a difference in the side by side boxplots 
```


#Plot of the EBLUPS for the random intercept
```{r}
qqnorm(ranef(hcovmod3)$intvid[,1]) 
qqline(ranef(hcovmod3)$intvid[,1])
```


#Binned residual plot
```{r}
library(arm)
dat12c_hd$phat<-predict(hcovmod3,type="response")
dat12c_hd$resid<-resid(hcovmod3,type="response")

binnedplot(dat12c_hd$phat,dat12c_hd$resid)
```

#AUC
```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE, fig.show='hide'}
#trying a different way to plot AUC with value
library(ROCR)

# Create prediction object
m1.prediction <- prediction(dat12c_hd$phat, dat12c_hd$hlthcov1)

# Calculate AUC value
m1.auc <- performance(m1.prediction, "auc")@y.values[[1]]
m1.auc

# Plot ROC curve
m1.perf <- performance(m1.prediction, "tpr", "fpr")
plot(m1.perf, main = "ROC Curve of Exercise", col = "blue", lwd = 2)
abline(a = 0, b = 1, lty = 2, lwd = 2)
legend("bottomright", legend = paste("AUC = ", round(m1.auc, 2)), col = "blue", lwd = 2, bty = "n")

#31%
```

```{r}
# Assuming your model is stored in 'mixed_model'
eblups1 <- ranef(hcovmod3)$intvid

# Extract EBLUPs as a numeric vector
eblup_values1 <- as.numeric(unlist(eblups1))

# Create a boxplot to visualize the distribution
plot(eblup_values1, main = "Distribution of EBLUPs for Any Health Coverage", ylab = "EBLUPs")
```







################### Tables and Figures####################################

#ICC tables

#For general health
```{r}
# Assuming you have a vector of ICC values
icc_values1 <- c(0.03, 0.05, 0.04, 0.01)

# Assuming you have a vector of workload categories
workload_categories <- c("Low", "Medium", "High", "Very High")

# Create a data frame
data1 <- data.frame(Workload = workload_categories, ICC1 = icc_values1)

# Plot the barplot
barplot(data1$ICC1, names.arg = data1$Workload, col = "lightblue", main = "ICC of Workload Groups for Self-rated General Health", xlab = "Workload Groups", ylab = "ICC")

# Add ICC values on top of each bar
text(x = barplot(data1$ICC1, col = "blue", plot = FALSE), y = data1$ICC1, label = round(data1$ICC1, 2), pos = 1.5, cex = 0.8, col = "black")
```

#for Depression
```{r}
# Assuming you have a vector of ICC values
icc_values2 <- c(0.00, 0.01, 0.01, 0.02)

# Assuming you have a vector of workload categories
workload_categories <- c("Low", "Medium", "High", "Very High")

# Create a data frame
data2 <- data.frame(Workload = workload_categories, ICC2 = icc_values2)

# Plot the barplot
barplot(data2$ICC2, names.arg = data2$Workload, col = "lightblue", main = "ICC of Workload Groups for Any Depression", xlab = "Workload Groups", ylab = "ICC")

# Add ICC values on top of each bar
text(x = barplot(data2$ICC2, col = "blue", plot = FALSE), y = data2$ICC2, label = round(data2$ICC2, 2), pos = 1.5, cex = 0.8, col = "black")
```

#for Exercise
```{r}
# Assuming you have a vector of ICC values
icc_values3 <- c(0.04, 0.04, 0.03, 0.02)

# Assuming you have a vector of workload categories
workload_categories <- c("Low", "Medium", "High", "Very High")

# Create a data frame
data3 <- data.frame(Workload = workload_categories, ICC3 = icc_values3)

# Plot the barplot
barplot(data3$ICC3, names.arg = data3$Workload, col = "lightblue", main = "ICC of Workload Groups for Any Exercise", xlab = "Workload Groups", ylab = "ICC")

# Add ICC values on top of each bar
text(x = barplot(data3$ICC3, col = "blue", plot = FALSE), y = data3$ICC3, label = round(data3$ICC3, 2), pos = 1.5, cex = 0.8, col = "black")
```

#for health coverage
```{r}
# Assuming you have a vector of ICC values
icc_values4 <- c(0.03, 0.02, 0.05, 0.08)

# Assuming you have a vector of workload categories
workload_categories <- c("Low", "Medium", "High", "Very High")

# Create a data frame
data4 <- data.frame(Workload = workload_categories, ICC4 = icc_values4)

# Plot the barplot
barplot(data4$ICC4, names.arg = data4$Workload, col = "lightblue", main = "ICC of Workload Groups for Any Health coverage", xlab = "Workload Groups", ylab = "ICC")

# Add ICC values on top of each bar
text(x = barplot(data4$ICC4, col = "blue", plot = FALSE), y = data4$ICC4, label = round(data4$ICC4, 2), pos = 1.5, cex = 0.8, col = "black")
```


#Checking workload levels for the 4 outcome variables
```{r}
table(dat12c_hd$genhlth2, dat12c_hd$wkl) 
table(dat12c_hd$hlthcov1, dat12c_hd$wkl) 
table(dat12c_hd$depr1, dat12c_hd$wkl) 
table(dat12c_hd$exer1, dat12c_hd$wkl) 
```
For each of the four outcome variables, the total are the same and totals to the overall workload level

#Calculating the length of questions

#counting characters
```{r}
nchar("Would you say that in general your health is")
```

#counting words
```{r}
library(stringi)

genhlthwords <- stri_count_words("Would you say that in general your health is")
genhlthwords #9

hcovwords <- stri_count_words("Do you have any kind of health care coverage, including health   insurance, prepaid plans such as HMOs, government plans such as Medicare, or Indian Health Service?")
hcovwords #26

deprwords <- stri_count_words("During the past month, other than your regular job, did you participate in any physical activities or exercises such as running, calisthenics, golf, gardening, or walking for exercise?")
deprwords #28

exerwords <- stri_count_words("Now thinking about your mental health, which includes stress, depression, and problems with emotions, for how many days during the past 30 days was your mental health not good")
exerwords #29
```

#Creating icc table across workloads to address paper feedback
```{r}
icc_low <- c(0.03, 0.00, 0.04, 0.03)

low_outcomes <- c("SRH", "Depression", "Exercise", "Health coverage")

# Create a data frame
datanew <- data.frame(outcomes = low_outcomes, iccL = icc_low)

# Plot the barplot
barplot(datanew$iccL, names.arg = datanew$outcomes, col = "lightyellow", main = "ICC in Low Workload Group", xlab = "Health Outcomes", ylab = "ICC")

# Add ICC values on top of each bar
text(x = barplot(datanew$iccL, col = "blue", plot = FALSE), y = datanew$iccL, label = round(datanew$iccL, 2), pos = 1.5, cex = 0.8, col = "black")
```

```{r}
# Define the data
icc_low1 <- c(0.03, 0.00, 0.04, 0.03)
low_outcomes1 <- c("SRH", "Depression", "Exercise", "Health coverage")

# Create a data frame
datanew1 <- data.frame(outcomes = low_outcomes1, iccL = icc_low1)

# Create the plot
plot(icc_low1, type = "o", col = "violet", ylim = c(0, max(icc_low1) + 0.05), 
     main = "ICC in Low Workload Group", xlab = "Health Outcomes", ylab = "ICC")

# Add the labels
text(1:length(low_outcomes1), icc_low1, labels = round(icc_low1, 2), pos = 3, col = "black")

# Add the x-axis ticks and labels
#axis(1, at = 1:length(low_outcomes1), labels = low_outcomes1)

axis(1, at = 1:length(low_outcomes1), labels = low_outcomes1, tick = FALSE)

```

#LOW WORKLOAD
```{r}
# Define the data
icc_low1 <- c(0.00, 0.03, 0.03, 0.04)
low_outcomes1 <- c("Depression", "Self-rated General Health", "Health coverage", "Exercise")

# Create a data frame
datanew1 <- data.frame(outcomes = low_outcomes1, iccL = icc_low1)

# Create the plot without x-axis
plot(icc_low1, type = "o", col = "darkgreen", ylim = c(0, max(icc_low1) + 0.05), 
     main = "ICC in Low Workload Group", xlab = "", ylab = "ICC", xaxt = "n", lwd = 2)

# Add the labels
text(1:length(low_outcomes1), icc_low1, labels = round(icc_low1, 2), pos = 3, col = "black")

# Add custom x-axis with just the labels
axis(1, at = 1:length(low_outcomes1), labels = low_outcomes1, tick = FALSE)
```


#MEDIUM WORKLOAD
```{r}
# Define the data
icc_med <- c(0.01, 0.02, 0.04, 0.05)
med_outcomes <- c("Depression", "Health coverage", "Exercise", "Self-rated general health")

# Create a data frame
datanew2 <- data.frame(outcomes = med_outcomes, iccM = icc_med)

# Create the plot without x-axis
plot(icc_med, type = "o", col = "darkgreen", ylim = c(0, max(icc_med) + 0.05), 
     main = "ICC in Medium Workload Group", xlab = "", ylab = "ICC", xaxt = "n", lwd = 2)

# Add the labels
text(1:length(med_outcomes), icc_med, labels = round(icc_med, 2), pos = 3, col = "black")

# Add custom x-axis with just the labels
axis(1, at = 1:length(med_outcomes), labels = med_outcomes, tick = FALSE)
```

#HIGH WORKLOAD
```{r}
# Define the data
icc_high <- c(0.01, 0.03, 0.04, 0.05)
hi_outcomes <- c("Depression", "Exercise", "Self-rated general health", "Health coverage")

# Create a data frame
datanew3 <- data.frame(outcomes = hi_outcomes, iccH = icc_high)

# Create the plot without x-axis
plot(icc_high, type = "o", col = "darkgreen", ylim = c(0, max(icc_high) + 0.05), 
     main = "ICC in High Workload Group", xlab = "", ylab = "ICC", xaxt = "n", lwd = 2)

# Add the labels
text(1:length(hi_outcomes), icc_high, labels = round(icc_high, 2), pos = 3, col = "black")

# Add custom x-axis with just the labels
axis(1, at = 1:length(hi_outcomes), labels = hi_outcomes, tick = FALSE)
```


#VERY HIGH WORKLOAD
```{r}
# Define the data
icc_vh <- c(0.01, 0.02, 0.02, 0.08)
vh_outcomes <- c("Self-rated general health", "Depression", "Exercise", "Health coverage")

# Create a data frame
datanew4 <- data.frame(outcomes = vh_outcomes, iccH = icc_vh)

# Create the plot without x-axis
plot(icc_vh, type = "o", col = "darkgreen", ylim = c(0, max(icc_vh) + 0.05), 
     main = "ICC in Very High Workload Group", xlab = "", ylab = "ICC", xaxt = "n", lwd = 2)

# Add the labels
text(1:length(vh_outcomes), icc_vh, labels = round(icc_vh, 2), pos = 3, col = "black")

# Add custom x-axis with just the labels
axis(1, at = 1:length(vh_outcomes), labels = vh_outcomes, tick = FALSE)
```



#################DECEMBER 2012#########################

```{r}
dat12cM <- dat12c_hd %>% 
  filter(imonth == 12)
```


#with general health

#FOR LOW WORKLOAD
```{r}
dat12c_lowM <- dat12cM %>%
            filter(wkl=="Low")

```

```{r}
modgen1LowM <- glmer(genhlth2 ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_lowM)

summary(modgen1LowM)
#intercept not sig
```

#icc for Low
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance1 <- VarCorr(modgen1LowM)$intvid[1]

# Calculate ICC
icc1m <- random_intercept_variance1 / (random_intercept_variance1 + pi^2 / 3)
icc1m
#0.06
```

#FOR MEDIUM WORKLOAD
```{r}
dat12c_MedM <- dat12cM %>%
            filter(wkl=="Medium")

```

```{r}
modgen1MedM <- glmer(genhlth2 ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_MedM)

summary(modgen1MedM)
#intercept sig
```

#icc for MEDIUM
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance2 <- VarCorr(modgen1MedM)$intvid[1]

# Calculate ICC
icc2m <- random_intercept_variance2 / (random_intercept_variance2 + pi^2 / 3)
icc2m
#0.01
```

#FOR HIGH WORKLOAD
```{r}
dat12c_HM <- dat12cM %>%
            filter(wkl=="High")

```

```{r}
modgen1HM <- glmer(genhlth2 ~ 1 + (1 | intvid),
                  weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_HM)

summary(modgen1HM)
#intercept sig
```

#icc for HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance3 <- VarCorr(modgen1HM)$intvid[1]

# Calculate ICC
icc3m <- random_intercept_variance3 / (random_intercept_variance3 + pi^2 / 3)
icc3m
#0.03
```


#FOR VERY HIGH WORKLOAD
```{r}
dat12c_VHM <- dat12cM %>%
            filter(wkl=="Very high")

```

```{r}
modgen1VHM <- glmer(genhlth2 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_VHM)

summary(modgen1VHM)
#intercept sig
```

#icc for VERY HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance4 <- VarCorr(modgen1VHM)$intvid[1]

# Calculate ICC
icc4m <- random_intercept_variance4 / (random_intercept_variance4 + pi^2 / 3)
icc4m
#0.02
```

#Chekcing ICC variation for Dec with Low data for genhealth
```{r}
# Load required libraries
library(dplyr) # for data manipulation
library(broom) # for tidying model outputs

# Identify unique interviewers
interviewers1 <- unique_countsLM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_lowM %>% filter(intvid != interviewers1[i])
  
  modgen1LowM1 <- glmer(genhlth2 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(modgen1LowM1)$intvid[1]

# Calculate ICC
icc4m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc4m1
}

# Print coefficients for each model
# for (i in 1:length(coefficients_list)) {
#   cat("Coefficients for model excluding interviewer", interviewers[i], ":\n")
#   print(coefficients_list[[i]])
#   cat("\n")
# }
mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for low workload of Self-rated general health")
```
mean ICC 0.04541858
no outlier

new mean ICC 0.04561488
new plot  ??

#Chekcing ICC variation for Dec with Medium data for genhealth
```{r}
# Identify unique interviewers
interviewers1 <- unique_countsMM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_MedM %>% filter(intvid != interviewers1[i])
  

  modgen1MedM1 <- glmer(genhlth2 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(modgen1MedM1)$intvid[1]

# Calculate ICC
icc4m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc4m1
}

mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for medium workload of Self-rated general health")
```
mean ICC 0.005658712
one outlier but not significant

new mean ICC 0.005283678
new plot few outliers

#Chekcing ICC variation for Dec with High data for genhealth
```{r}
# Identify unique interviewers
interviewers1 <- unique_countsHM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_HM %>% filter(intvid != interviewers1[i])
  
  modgen1HM1 <- glmer(genhlth2 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(modgen1HM1)$intvid[1]

# Calculate ICC
icc4m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc4m1
}

mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for high workload of Self-rated general health")
```
mean ICC 0.02904352
one outlier

new mean ICC 0.02918918
new plot very few outlier


#Chekcing ICC variation for Dec with VH data for genhealth
```{r}
# Identify unique interviewers
interviewers1 <- unique_countsVHM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_VHM %>% filter(intvid != interviewers1[i])
  
  modgen1VHM1 <- glmer(genhlth2 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(modgen1VHM1)$intvid[1]

# Calculate ICC
icc4m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc4m1
}

mean(coefficients_list)

genVH <- plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for very high workload of Self-rated general health")
```
mean ICC 0.01773435
couple of outliers

new mean ICC 0.01775556
new plot very few outliers

#WITH DEPRESSION

#FOR LOW WORKLOAD
```{r}
moddep1LowM <- glmer(depr1 ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_lowM)

summary(moddep1LowM)
#sig
#
moddep1LowMN <- glmer(depnew1 ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_lowM)

summary(moddep1LowMN)
```

#icc for Low
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance1 <- VarCorr(moddep1LowM)$intvid[1]

# Calculate ICC
icc1m <- random_intercept_variance1 / (random_intercept_variance1 + pi^2 / 3)
icc1m
#0
#
random_intercept_variance1N <- VarCorr(moddep1LowMN)$intvid[1]

# Calculate ICC
icc1mN <- random_intercept_variance1N / (random_intercept_variance1N + pi^2 / 3)
icc1mN
```

#FOR MEDIUM WORKLOAD
```{r}
moddep1MedM <- glmer(depr1 ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_MedM)

summary(moddep1MedM)
#sig
#
moddep1MedMN <- glmer(depnew1 ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_MedM)

summary(moddep1MedMN)
```

#icc for MEDIUM
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance2 <- VarCorr(moddep1MedM)$intvid[1]

# Calculate ICC
icc2m <- random_intercept_variance2 / (random_intercept_variance2 + pi^2 / 3)
icc2m
#0.00
#
random_intercept_variance2N <- VarCorr(moddep1MedMN)$intvid[1]

# Calculate ICC
icc2mN <- random_intercept_variance2N / (random_intercept_variance2N + pi^2 / 3)
icc2mN
```

#FOR HIGH WORKLOAD
```{r}
moddep1HM <- glmer(depr1 ~ 1 + (1 | intvid),
                  weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_HM)

summary(moddep1HM)
#intercept sig
#
moddep1HMN <- glmer(depnew1 ~ 1 + (1 | intvid),
                  weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_HM)

summary(moddep1HMN)
```

#icc for HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance3 <- VarCorr(moddep1HM)$intvid[1]

# Calculate ICC
icc3m <- random_intercept_variance3 / (random_intercept_variance3 + pi^2 / 3)
icc3m
#0.0
#
random_intercept_variance3N <- VarCorr(moddep1HMN)$intvid[1]

# Calculate ICC
icc3mN <- random_intercept_variance3N / (random_intercept_variance3N + pi^2 / 3)
icc3mN
#5.300357e-05
```


#FOR VERY HIGH WORKLOAD
```{r}
moddep1VHM <- glmer(depr1 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_VHM)

summary(moddep1VHM)
#intercept sig
#
moddep1VHMN <- glmer(depnew1 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_VHM)

summary(moddep1VHMN)
```

#icc for VERY HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance4 <- VarCorr(moddep1VHM)$intvid[1]

# Calculate ICC
icc4m <- random_intercept_variance4 / (random_intercept_variance4 + pi^2 / 3)
icc4m
#0
#
random_intercept_variance4N <- VarCorr(moddep1VHMN)$intvid[1]

# Calculate ICC
icc4mN <- random_intercept_variance4N / (random_intercept_variance4N + pi^2 / 3)
icc4mN
#0
```

#Chekcing ICC variation for Dec with low data for any depression
```{r}
# Identify unique interviewers
interviewers1 <- unique_countsLM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_lowM %>% filter(intvid != interviewers1[i])
  
  moddep1LowM1 <- glmer(depnew1 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(moddep1LowM1)$intvid[1]

# Calculate ICC
icc3m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc3m1
}

mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for Low Workload of Any Depression")
```
mean ICC 0
no outlier

new mean ICC 0
new plot no outlier

4.036721e-18


#Chekcing ICC variation for Dec with medium data for any depression
```{r}
# Identify unique interviewers
interviewers1 <- unique_countsMM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_MedM %>% filter(intvid != interviewers1[i])
  
  moddep1MedM1 <- glmer(depnew1 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(moddep1MedM1)$intvid[1]

# Calculate ICC
icc3m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc3m1
}

mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for Medium Workload of Any Depression")
```
mean ICC 0.001964791
no outlier
scattered

new mean ICC 0.002004233
new plot not significant outlier

0.002004226

#Chekcing ICC variation for Dec with high data for any depression
```{r}
# Identify unique interviewers
interviewers1 <- unique_countsHM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_HM %>% filter(intvid != interviewers1[i])
  
  moddep1HM1 <- glmer(depnew1 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(moddep1HM1)$intvid[1]

# Calculate ICC
icc3m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc3m1
}

mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for High Workload of Any Depression")
```
mean ICC 0.0006376662
outlier

new mean ICC 0.000759813
new plot few outliers

0.000759801

#Chekcing ICC variation for Dec with very high data for any depression
```{r}
# Identify unique interviewers
interviewers1 <- unique_countsVHM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_VHM %>% filter(intvid != interviewers1[i])
  
  moddep1VHM1 <- glmer(depnew1 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(moddep1VHM1)$intvid[1]

# Calculate ICC
icc3m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc3m1
}

mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for Very High Workload of Any Depression")
```
mean ICC 3.922692e-14
one outlier
scattered 

new mean ICC 7.86619e-14
new plot one outlier

4.291336e-14


#WITH EXERCISE

#FOR LOW WORKLOAD
```{r}
modex1LowM <- glmer(exernew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_lowM)

summary(modex1LowM)
#sign
#
modex1LowMN <- glmer(exernew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_lowM)

summary(modex1LowMN)
```

#icc for Low
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance1 <- VarCorr(modex1LowM)$intvid[1]

# Calculate ICC
icc1m <- random_intercept_variance1 / (random_intercept_variance1 + pi^2 / 3)
icc1m
#0.07
#
random_intercept_variance1N <- VarCorr(modex1LowMN)$intvid[1]

# Calculate ICC
icc1mN <- random_intercept_variance1N / (random_intercept_variance1N + pi^2 / 3)
icc1mN
```

#FOR MEDIUM WORKLOAD
```{r}
modex1MedM <- glmer(exer1 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_MedM)

summary(modex1MedM)
#sign
#
modex1MedMN <- glmer(exernew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_MedM)

summary(modex1MedMN)
```

#icc for MEDIUM
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance2 <- VarCorr(modex1MedM)$intvid[1]

# Calculate ICC
icc2m <- random_intercept_variance2 / (random_intercept_variance2 + pi^2 / 3)
icc2m
#0
#
random_intercept_variance2N <- VarCorr(modex1MedMN)$intvid[1]

# Calculate ICC
icc2mN <- random_intercept_variance2N / (random_intercept_variance2N + pi^2 / 3)
icc2mN
```

#FOR HIGH WORKLOAD
```{r}
modex1HM <- glmer(exer1 ~ 1 + (1 | intvid),
                 weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_HM)

summary(modex1HM)
#intercept sig
#
#
modex1HMN <- glmer(exernew ~ 1 + (1 | intvid),
                 weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_HM)

summary(modex1HMN)
```

#icc for HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance3 <- VarCorr(modex1HM)$intvid[1]

# Calculate ICC
icc3m <- random_intercept_variance3 / (random_intercept_variance3 + pi^2 / 3)
icc3m
#0.07
#
random_intercept_variance3N <- VarCorr(modex1HMN)$intvid[1]

# Calculate ICC
icc3mN <- random_intercept_variance3N / (random_intercept_variance3N + pi^2 / 3)
icc3mN
```


#FOR VERY HIGH WORKLOAD
```{r}
modex1VHM <- glmer(exer1 ~ 1 + (1 | intvid),
                  weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_VHM)

summary(modex1VHM)
#intercept sig
#
modex1VHMN <- glmer(exernew ~ 1 + (1 | intvid),
                  weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_VHM)

summary(modex1VHMN)
```

#icc for VERY HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance4 <- VarCorr(modex1VHM)$intvid[1]

# Calculate ICC
icc4m <- random_intercept_variance4 / (random_intercept_variance4 + pi^2 / 3)
icc4m
#0.04
#
random_intercept_variance4N <- VarCorr(modex1VHMN)$intvid[1]

# Calculate ICC
icc4mN <- random_intercept_variance4N / (random_intercept_variance4N + pi^2 / 3)
icc4mN
```

#Chekcing ICC variation for Dec with low data for any exercise
```{r}
# Identify unique interviewers
interviewers1 <- unique_countsLM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_lowM %>% filter(intvid != interviewers1[i])
  
  modgen1LowM1 <- glmer(exernew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(modgen1LowM1)$intvid[1]

# Calculate ICC
icc2m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc2m1
}

mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for Low Workload of Any Exercise")
```
mean ICC 0.06032196
no outlier

new mean ICC 0.05830256
new plot some outliers

0.05830255

#Chekcing ICC variation for Dec with medium data for any exercise
```{r}
# Identify unique interviewers
interviewers1 <- unique_countsMM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_MedM %>% filter(intvid != interviewers1[i])
  
  modgen1MedM1 <- glmer(exernew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(modgen1MedM1)$intvid[1]

# Calculate ICC
icc2m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc2m1
}

mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for Medium Workload of Any Exercise")
```
mean ICC 0.004362907
one outlier but not significant

new mean ICC 0.004595576
new plot few outliers

0.004595571

#Chekcing ICC variation for Dec with high data for any exercise
```{r}
# Identify unique interviewers
interviewers1 <- unique_countsHM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_HM %>% filter(intvid != interviewers1[i])
  
  modgen1HM1 <- glmer(exernew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(modgen1HM1)$intvid[1]

# Calculate ICC
icc2m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc2m1
}

mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for High Workload of Any Exercise")
```
mean ICC 0.06589049
couple of outliers 

new mean ICC 0.06598516
new plot outliers

0.06598515

#Chekcing ICC variation for Dec with very high data for any exercise
```{r}
# Identify unique interviewers
interviewers1 <- unique_countsVHM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_VHM %>% filter(intvid != interviewers1[i])
  
  modgen1VHM1 <- glmer(exernew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(modgen1VHM1)$intvid[1]

# Calculate ICC
icc2m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc2m1
}

mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for Very High Workload of Any Exercise")
```
mean ICC 0.04245941
few outliers

new mean ICC 0.04252395
new plot few outliers

0.04252395

#FOR HEALTH COVERAGE

#FOR LOW WORKLOAD
```{r}
modhcovLowM <- glmer(hcov ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_lowM)

summary(modhcovLowM)


modhcovLowMN <- glmer(hcovnew ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_lowM)

summary(modhcovLowMN)

```

#icc for Low
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance1 <- VarCorr(modhcovLowM)$intvid[1]

# Calculate ICC
icc1m <- random_intercept_variance1 / (random_intercept_variance1 + pi^2 / 3)
icc1m
#0.0
#
#
random_intercept_variance1N <- VarCorr(modhcovLowMN)$intvid[1]

# Calculate ICC
icc1mN <- random_intercept_variance1N / (random_intercept_variance1N + pi^2 / 3)
icc1mN
#0
```

#FOR MEDIUM WORKLOAD
```{r}
modhcovMedM <- glmer(hlthcov1 ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_MedM)

summary(modhcovMedM)

modhcovMedMN <- glmer(hcovnew ~ 1 + (1 | intvid),
                    weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_MedM)

summary(modhcovMedMN)

```

#icc for MEDIUM
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance2 <- VarCorr(modhcovMedM)$intvid[1]

# Calculate ICC
icc2m <- random_intercept_variance2 / (random_intercept_variance2 + pi^2 / 3)
icc2m
#0.0
#
random_intercept_variance2N <- VarCorr(modhcovMedMN)$intvid[1]

# Calculate ICC
icc2mN <- random_intercept_variance2N / (random_intercept_variance2N + pi^2 / 3)
icc2mN
#0
```

#FOR HIGH WORKLOAD
```{r}
modhcovHM <- glmer(hlthcov1 ~ 1 + (1 | intvid),
                  weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_HM)

summary(modhcovHM)
#intercept sig
#
#
modhcovHMN <- glmer(hcovnew ~ 1 + (1 | intvid),
                  weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_HM)

summary(modhcovHMN)
```

#icc for HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance3 <- VarCorr(modhcovHM)$intvid[1]

# Calculate ICC
icc3 <- random_intercept_variance3 / (random_intercept_variance3 + pi^2 / 3)
icc3
#0.01
#
random_intercept_variance3N <- VarCorr(modhcovHMN)$intvid[1]

# Calculate ICC
icc3N <- random_intercept_variance3N / (random_intercept_variance3N + pi^2 / 3)
icc3N
#0.01
```


#FOR VERY HIGH WORKLOAD
```{r}
modhcovVH <- glmer(hlthcov1 ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_VHWL)

summary(modhcovVH)
#intercept sig
#
modhcovVHN <- glmer(hcovnew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = dat12c_VHWL)

summary(modhcovVHN)
```

#icc for VERY HIGH
```{r}
# Extract variance of the random intercept from the model
random_intercept_variance4 <- VarCorr(modhcovVH)$intvid[1]

# Calculate ICC
icc4 <- random_intercept_variance4 / (random_intercept_variance4 + pi^2 / 3)
icc4
#0.08
#
random_intercept_variance4N <- VarCorr(modhcovVHN)$intvid[1]

# Calculate ICC
icc4N <- random_intercept_variance4N / (random_intercept_variance4N + pi^2 / 3)
icc4N
#0.08
```


#Chekcing ICC variation for Dec with low data for any health coverage
```{r}
#dat12c_lowM$intvid_state <- paste(dat12c_lowM$intvid, dat12c_lowM$state, sep = "_")

# Identify unique interviewers including state information
interviewers1 <- unique_countsLM$intvid

# Identify unique interviewers
#interviewers <- unique(dat12c_lowM$intvid)

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_lowM %>% filter(intvid != interviewers1[i])
  
  modhcov1LowM1 <- glmer(hcovnew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(modhcov1LowM1)$intvid[1]

# Calculate ICC
icc1m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc1m1
}

mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for Low Workload of Any Health Coverage")
```
mean ICC 0.018995
one outlier 

new mean icc 0.01582917
new plot 6 outliers

0.01582917

#Chekcing ICC variation for Dec with medium data for any health coverage
```{r}
#dat12c_MedM$intvid_state1 <- paste(dat12c_MedM$intvid, dat12c_MedM$state, sep = "_")
# Identify unique interviewers
#interviewers <- unique(dat12c_MedM$intvid)
#
# Identify unique interviewers including state information
interviewers1 <- unique_countsMM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_MedM %>% filter(intvid != interviewers1[i])
  
  modhcov1MedM1 <- glmer(hcovnew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(modhcov1MedM1)$intvid[1]

# Calculate ICC
icc1m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc1m1
}

mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for Medium Workload of Any Health Coverage")
```
mean ICC 7.746634e-16
one outlier 

new mean icc 5.620107e-16
new plot few outliers

8.316439e-16

#Chekcing ICC variation for Dec with high data for any health coverage
```{r}
# Identify unique interviewers
interviewers1 <- unique_countsHM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_HM %>% filter(intvid != interviewers1[i])
  
  modhcov1HM1 <- glmer(hcovnew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(modhcov1HM1)$intvid[1]

# Calculate ICC
icc1m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc1m1
}

mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for High Workload of Any Health Coverage")
```
mean ICC 0.01417939
one outlier

new mean icc 0.01427636
new plot few outliers

0.01427636

#Chekcing ICC variation for Dec with very high data for any health coverage
```{r}
# Identify unique interviewers
interviewers1 <- unique_countsVHM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_VHM %>% filter(intvid != interviewers1[i])
  
  modhcov1VHM1 <- glmer(hcovnew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(modhcov1VHM1)$intvid[1]

# Calculate ICC
icc1m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc1m1
}

mean(coefficients_list)

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for Very High Workload of Any Health Coverage")
```
mean ICC 0.09016529
few outliers

new mean icc 0.09023645
new plot some outliers

0.09023649


#removing intvids
```{r}
# Identify unique interviewers
interviewers1 <- unique_countsVHM$intvid

# Create an empty list to store coefficients
coefficients_list <- c()

# Loop through each interviewer
for (i in 1:length(interviewers1)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_VHM %>% filter(intvid != interviewers1[i])
  
  modhcov1VHM1 <- glmer(hcovnew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41 <- VarCorr(modhcov1VHM1)$intvid[1]

# Calculate ICC
icc1m1 <- random_intercept_variance41 / (random_intercept_variance41 + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list[i] <- icc1m1
}

mean(coefficients_list)

# Filter coefficients_list to exclude values less than or equal to 0.088
filtered_coefficients <- coefficients_list[coefficients_list > 0.088]

# Calculate the mean of the filtered coefficients
mean_filtered <- mean(filtered_coefficients)

# Display the mean of the filtered coefficients
print(mean_filtered)

plot(filtered_coefficients, ylim=c(0,0.15) ,xlab = "Interviewer ID", ylab = "ICC for Very High Workload of Any Health Coverage filtered")
```
0.09037814


#trying to remove interviewers
```{r}
# Identify unique interviewers
interviewers2 <- unique_countsVHM$intvid[-c(192, 193, 263, 270, 270, 535, 536, 537, 869, 870, 871, 893, 895, 896, 1028, 1029, 1030, 1190, 1191)]

# Create an empty list to store coefficients
coefficients_list1 <- c()

# Loop through each interviewer
for (i in 1:length(interviewers2)) {
  # Subset data excluding the current interviewer
  subset_data <- dat12c_VHM %>% filter(intvid != interviewers2[i])
  
  modhcov1VHM1 <- glmer(hcovnew ~ 1 + (1 | intvid),
                   weights = wt3>0,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa"),
  nAGQ = 1,
  data = subset_data)

# Extract variance of the random intercept from the model
random_intercept_variance41a <- VarCorr(modhcov1VHM1)$intvid[1]

# Calculate ICC
icc1m1a <- random_intercept_variance41a / (random_intercept_variance41a + pi^2 / 3)

  
  # Store coefficients in the list
  coefficients_list1[i] <- icc1m1a
}

mean(coefficients_list1)

plot(coefficients_list1, xlab = "Interviewer ID", ylim=c(0,0.1), ylab = "ICC for Very High Workload of Any Health Coverage after removing ints")

#number of ints of the outliers
outlierints <- which(coefficients_list1<=0.086)

#icc for <0.086
coefficients_list[which(coefficients_list<=0.086)]

# Filter coefficients_list to exclude values less than or equal to 0.088
filtered_coefficients <- coefficients_list[coefficients_list > 0.088]

plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for Very High Workload of Any Health Coverage")
```

0.09031028


```{r}
unique_countsLM <- dat12c_lowM %>% 
  group_by(intvid, state) %>% 
  summarise(count = n())

# Count the number of unique interviewers
num_unique_interviewersLM <- nrow(unique_countsLM)
num_unique_interviewersLM
```
36

```{r}
unique_countsMM <- dat12c_MedM %>% 
  group_by(intvid, state) %>% 
  summarise(count = n())

# Count the number of unique interviewers
num_unique_interviewersMM <- nrow(unique_countsMM)
num_unique_interviewersMM
```
153

```{r}
unique_countsHM <- dat12c_HM %>% 
  group_by(intvid, state) %>% 
  summarise(count = n())

# Count the number of unique interviewers
num_unique_interviewersHM <- nrow(unique_countsHM)
num_unique_interviewersHM
```
504

```{r}
unique_countsVHM <- dat12c_VHM %>% 
  group_by(intvid, state) %>% 
  summarise(count = n())

# Count the number of unique interviewers
num_unique_interviewersVHM <- nrow(unique_countsVHM)
num_unique_interviewersVHM
```
1726

```{r}
unique_countsM <- dat12cM %>% 
  group_by(intvid, state) %>% 
  summarise(count = n())

# Count the number of unique interviewers
num_unique_interviewersM <- nrow(unique_countsM)
num_unique_interviewersM
```
2419

```{r}
# par(mfrow=c(1,3))
# genVH
# plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for Very High Workload of Any Health Coverage")
# plot(coefficients_list, xlab = "Interviewer ID", ylab = "ICC for Very High Workload of Any Health Coverage")
```

```{r}
dat12c_hd$depnew <- as.numeric(dat12c_hd$depr1)
table(dat12c_hd$depnew)
```

